# ```OpinionReport```

```OpinionReport``` is an R package that includes utility to plot AbridgeNews reaction data.

# Getting started

### Install ```OpinionReport```
In R or RStudio, install the ```OpinionReport``` R package from github.  

#### Install and load ```devtools```
```
install.packages( c('devtools'))
library(devtools)
```

#### Install and load ```OpinionReport```
```{r}
devtools::install_github('lhenneman/OpinionReport')
library(OpinionReport)
```

# Define the data
```OpinionReport``` includes a utility, ```OpData``` that takes as inputs all the relavent information for a topic and saves a .csv file that can later be imported to the plotting function. The information is defined as follows:

### Opinion data
Opinion data must be provided for the *Left Side* (**LS**), *mid Left Side* (**mLS**), *mid Right Side* (**mRS**), and *Right Side* (**RS**). OpinionData for each article should be provided as a named vector with three entries, "Agree", "Disagree", and "Undecided".

### Names
Names (```LSname```, ```mLSname```, etc.) should be provided as text strings, but do not need to be provided if you prefer the column labels to be left blank (e.g., ```mLS``` and ```mRS``` are often left blank). If you want to have line breaks included in the eventual plot, use "```/n```". In the command below, the Left Side name (```LSname```) is provided with line break between "Remove" and "Silent", the Right Side name (```RSname```) is provided with line break between "Keep" and "Silent", and no names are provided for ```mLSname``` or ```mRSname```.

### Topic title (file name)
The ```topictitle``` describes the day's topic in a short unique phrase without spaces that will be used as a base file name for both the .csv file and the eventual plot.

### Output directory
```outdir``` points to the saving location of the .csv file.

```{r}
OpData( LSname = 'Remove\nSilent Sam',
        RSname = 'Keep\nSilent Sam',
        LSopinion = c(  'Agree'      = 28,
                        'Disagree'   = 12,
                        'Undecided'  = 6 ),
        mLSopinion = c( 'Agree'      = 21,
                        'Disagree'   = 13,
                        'Undecided'  = 10 ),
        mRSopinion = c( 'Agree'      = 20,
                        'Disagree'   = 11,
                        'Undecided'  = 14 ),
        RSopinion = c(  'Agree'      = 19,
                        'Disagree'   = 25,
                        'Undecided'  = 6 ),
        title = 'silentsam',
        outdir = '.')
```

# Make the plot





The ```colorbounds``` describe the left and right colors on the topic's spectrum. 
```{r}
political.colbounds <- c("#1028C7", "#E8273A")
unc.colbounds <- c("#4f9ccf", "#162e4e")

colbounds <- unc.colbounds
```


















