# ```OpinionReport```

```OpinionReport``` is an R package that includes utility to plot AbridgeNews reaction data.

# Getting started

### Install ```OpinionReport```
In R or RStudio, install the ```OpinionReport``` R package from github.  

#### Install and load ```devtools```
```
install.packages( c('devtools'))
library(devtools)
```

#### Install and load ```OpinionReport```
```{r}
devtools::install_github('lhenneman/OpinionReport')
library(OpinionReport)
```

# Define the data
```OpinionReport``` includes a utility, ```OpData``` that takes as inputs all the relavent information for a topic and saves a .csv file that can later be imported to the plotting function. The information is defined as follows:

The ```topictitle``` describes the day's topic in a short unique phrase without spaces that will be used as a base file name for both the .csv file and the eventual plot.
```{r}
topictitle <- 'silentsam'
```

The ```colorbounds``` describe the left and right colors on the topic's spectrum. 
```{r}
political.colbounds <- c("#1028C7", "#E8273A")
unc.colbounds <- c("#4f9ccf", "#162e4e")

colbounds <- unc.colbounds
```

## Left side (LS)
```{r}
LSname <- 'Remove\nSilent Sam'
LSopinion <- c( 'Agree'      = 28,
                'Disagree'   = 12,
                'Undecided'  = 6 )
```

## Mid Left side (mLS)
```{r}
mLSname <- ' '
mLSopinion <- c( 'Agree'     = 21,
                 'Disagree'  = 13,
                 'Undecided' = 10 )
```

## Mid Right side (mRS)
```{r}
mRSname <- '  '
mRSopinion <- c( 'Agree'     = 20,
                 'Disagree'  = 11,
                 'Undecided' = 14 )
```

##Right side (mLS)
```{r}
RSname <- 'Keep\nSilent Sam'
RSopinion <- c( 'Agree'      = 19,
                'Disagree'   = 25,
                'Undecided'  = 6 )
```

## save a csv file with all the data
```{r}
OpData( LSname,
        mLSname,
        mRSname,
        RSname,
        LSopinion,
        mLSopinion,
        mRSopinion,
        RSopinion,
        title = topictitle,
        outdir = '~/Dropbox/HomeLife/Laura/AbridgeNews/OpinionReports/data')
```
























